---
title: "Alcohol vs Seat choice"
author: "Kaylie Brehm"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

## Is there a difference between the alcohol consumed and the row you choose to sit in??
$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.  

## Methods
To examine the average number of drinks students imbibed, numerical, conditioned on the row they sit in, categorical, I will do a numerical categorical analysis. I will also complete a T-Test to compare drink number in correlation to row sat in.


## Results

### Graphical Results
```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

Boxplot
```{r}
basicCN + geom_boxplot()
```

### Numerical Results

Numerical Chart
```{r}
favstats(alcohol~Seat,data=davisdata)
```

### Inferential Results

## Discussion and Conclusion


