---
title: "Alcohol vs Seat choice"
author: "Kaylie Brehm"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

## Is there a difference between the alcohol consumed and the row you choose to sit in??
$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.  

## Methods
To examine the average number of drinks students imbibed, numerical, conditioned on the row they sit in, categorical, I will do a numerical categorical analysis. I will also complete a T-Test to compare drink number in correlation to row sat in. The three categories for seat row are front, back, and center.


## Results

### Graphical Results
```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

Boxplot
```{r}
basicCN + geom_boxplot()
```

The graph shows a very low median number of drinks for each group, although they are different. The first quartile for each group is at or near zero. The back has a higher third quartile than the other two groups and therefore a larger interquartile range. The back group also has some extreme outliers. While the middle had moderate outliers and the front had little. The interquartile range is smallest in the front group.

### Numerical Results

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The mean for those in the back is 9.625000 and the median is 4. The median for the front is 0, and it is 1 for the middle. The mean for those in the front is 1.803030 and 3.283133 for middle. Based on these numbers, we can see a difference in average number of drinks for each row. 

### Inferential Results

AOV
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
This model shows some further information on standard deviation, mean and f value. Since the significance f value is so small, it rejects the null hypothesis.

```{r}
plot(TukeyHSD(model1))
```

This model provides a closer look into the calculated difference of means between each group. This piece of data alone allows me to reject the null hypothesis since there is an observably difference.

## Discussion and Conclusion

The inferential and numerical results allow me to reject the null hypothesis. There is a clear difference in mean, median, and standard deviation numbers for amount of drinks consumed in relation to seat position. Within the graphical results, we see a visual depiction of this. Whether or not drink values are dependent on seat placement, is up for debate. But, I can say for certain that there is a different in average drink number in at least two rows.
